The perceptual dimensions of \\ sonority-driven epenthesis

### 2013-09-30 paper.tex
Improved third diagram

\ex. \begin{tikzpicture} [shorten >=1pt,scale=0.33]
                      \draw [<-] (-3,6.5) -- (-3, 0.5) ; % axis
                      \node at (-3, 7.0) {Sonority}; % axis label
					  % left diagram
                      \draw (5,1) -- (0,3) -- (5,6) ; % 
                      \node at (1.8, 3.2) {$\theta$}; % 
                      \node[left] at  (0,3) {C$_1$}; 
                      \node[right] at (5,1) {C$_2$};
                      \node[right] at (5,6) {V};
					  % right diagram
                      \draw (20,3) -- (15,5) -- (20,6) ; % rising sonority
                      \node at (18, 4.8) {$\theta$}; % theta label for falling sonority
                      \node[left] at (15,5) {C$_1$}; 
                      \node[right] at (20,3) {C$_2$};
                      \node[right] at (20,6) {V};
\end{tikzpicture}

When C\textsubscript{1} (and, by extension, C\textsubscript{2}) is of higher sonority, as on the right, the VC\textsubscript{1}C\textsubscript{2} angle is clearlysmaller. The first term in the formula confirms the relation between the sonority of C\textsubscript{1} in terms of its closeness to V, and {\sc Sonority Angle} as a whole.

>>>>

\newpage

\ex. Illustration: keeping C\textsubscript{1} -- C\textsubscript{2} fixed at 1, raising the sonority in cluster decreases the {\sc Sonority Angle}.

\vspace{-5em}
\begin{center}
\begin{tikzpicture} [shorten >=1pt,scale=0.33]
                      \draw [<-] (-3,12) -- (-3, 0.5) ; % axis
                      \node at (-3, 13.0) {Sonority}; % axis label
					 % left diagram
    \coordinate (A) at (0,4); % pivot - C1 - F * 3
    \coordinate (B) at (15,2); % C2 - T * 3
    \coordinate (C) at (15,12); % V
    \draw (B) -- (A) -- (C);
	\tkzMarkAngle[size=2.5cm](B,A,C);
	\tkzLabelAngle[pos=4](B,A,C){$\theta_1$};
    \coordinate (D) at (15,6); % another C2 - N * 3
    \coordinate (E) at (0,8); % another C1 - R * 3
    \draw (D) -- (E) -- (C);
	\tkzMarkAngle[size=2.5cm](D,E,C);
	\tkzLabelAngle[pos=4](D,E,C){$\theta_2$};

    \node[left] at  (A) {F}; 
    \node[right] at (B) {T};
    \node[right] at (C) {V};
    \node[right] at (D) {N};
    \node[left] at (E) {R};   
    \draw [->,dotted] (B) -- (D);
    \draw [->,dotted] (A) -- (E);
\end{tikzpicture} 
\end{center}

The first term in formula \ref{sonangle_formula} confirms the relation between the sonority of C\textsubscript{1} in terms of its closeness to V, and {\sc Sonority Angle} as a whole.
